\chapter{Introduction and Background Research}

% You can cite chapters by using '\ref{chapter1}', where the label must
% match that given in the 'label' command, as on the next line.
\label{chapter1}

% Sections and sub-sections can be declared using \section and \subsection.
% There is also a \subsubsection, but consider carefully if you really need
% so many layers of section structure.
\section{Introduction}

Self-driving cars are becoming more popular with the aim of reducing the number of accidents related to driving. However, unlike typical computer programs that follow a set of instructions, self-driving cars must learn to drive, which involves learning to steer, brake, and navigate in order to function within unseen and complicated environments. We can simulate this using virtual environments, which allow us to simulate custom real-world environments.

An application of reinforcement learning involves learning to drive through trial and error without prior instructions. The simulated car would crash thousands of times before it understands how to perform the driving task, this approach is slow, and wastes a lot of computational power.

Methods such as imitation learning exist where we can treat the AI agent like a student, by showing examples of good driving first, instead of letting it learn through trial and error. Another way of tackling this issue is through curriculum learning, where we can gradually increase the difficulty of tasks.

My project aims to explore these teaching strategies inside a realistic simulation platform where we can train an AI agent to perform driving tasks using efficient methods.

Here is an example of how to cite a reference using the numeric system \cite{parikh1980adaptive}.


% Must provide evidence of a literature review. Use sections
% and subsections as they make sense for your project.
\section{Literature review}

\subsection{Deep Reinforcement Learning}

\subsection{Sample Inefficiency}

\subsection{Imitation Learning}

\subsection{Curriculum Learning}

\subsection{Simulation Environment}